
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Keshav Mittal}} & Email: \href{mailto:keshav.mittal1105@gmail.com}{keshav.mittal1105@gmail.com}\\
  \href{}{Portfolio: } & Mobile:~~~+91-9413514915 \\
  \href{https://github.com/keshav-mittal}{Github: ~~https://github.com/keshav-mittal} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{~~Education}
\resumeSubHeadingListStart

      \resumeSubheading
      {National Institute of Technology, Hamirpur}{Hamirpur}
      {Bachelor of Technology in Computer Science and Engineering}{Dec 2021 - May 2025}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{GPA:} 9.07 / 10.0}}}
      \resumeSubHeadingListEnd

\vspace{-5pt}
\section{Skills Summary}
\resumeSubHeadingListStart
\resumeSubItem{Languages}{~~~~~~C++, Java, Python, HTML, CSS, JavaScript} 
\resumeSubItem{Frameworks}{~~~~Next.js, Spring Boot, React.js, Node.js, Express.js} 
\resumeSubItem{Tools}{~~~~~~~~~~~~~~Git, GitHub, Postman, Redis, Docker, Kubernetes, Terraform, SOLID, HLD, LLD, OOPS, DBMS, OS, CN} 
\resumeSubItem{Databases}{~~~~~~~~MongoDB, MySQL, PostgreSQL} 
\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Experience}
\resumeSubHeadingListStart

      \resumeSubheading{Ultimate Kronos Group (UKG)}{Noida, INDIA}
      {Software Development Engineer 1}{Aug 2025 - Present}
      \resumeItemListStart
        \resumeItemWithoutTitle{Re-architected a mission-critical payroll API by shifting from cache-based retrieval to PostgreSQL paginated querying (65k row chunks), eliminating timeout failures and reducing infrastructure cost.}
\resumeItemWithoutTitle{Created a GitHub Actions workflow to automate GCP secret migrations using Terraform, Python; required for the Deploy Service pipeline and project creation on GCP saved time (20 min/project).}
\resumeItemWithoutTitle{Building an AI diagnostic agent integrating Teams, GitHub, Jira, and PES APIs to surface swarm issues and accelerate root-cause identification.}
        \resumeItemListEnd
      
      \resumeSubheading{WebSonix}{Mumbai, INDIA}
      {Software Developer Intern}{May 2024 - Nov 2024}
      \resumeItemListStart
        \resumeItemWithoutTitle{Engineered and deployed an innovative web portal using ReactJS with Firebase backend services.}
\resumeItemWithoutTitle{Interacted with 200+ potential customers, preparing the product for launch and building community interest.}
\resumeItemWithoutTitle{Optimized performance by reducing response time from 3s to under 1s.}
        \resumeItemListEnd
      \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart

      \resumeSubItem{ResumeGenie.AI}{(React.js, TypeScript, Node.js, Express.js, shadcn/ui, Firebase, GenAI, Docker) \resumeItemListStart
        \resumeItemWithoutTitle{Architected an AI-powered resume platform with PDF parsing, LaTeX editing, and role-specific suggestions.}
\resumeItemWithoutTitle{Designed RESTful APIs in Node.js/Express for resume parsing and AI scoring, delivering 25 highly matched job recommendations per call.}
\resumeItemWithoutTitle{Integrated Firebase Auth for secure Google login and Firestore for managing editable LaTeX resume template.}
\resumeItemWithoutTitle{Crafted an n8n-based AI agent that scrapes live job listings with 70\%+ resume–JD match and surfaces direct application links.}
        \resumeItemListEnd}
      \vspace{2pt}
      
      \resumeSubItem{Legal-text Summarizer}{(Python, Spring Boot, HuggingFace, GenAI, Dropbox) \resumeItemListStart
        \resumeItemWithoutTitle{Fine-tuned a T5-based model for legal-text summarization through data preprocessing and task-specific training, improving summarization accuracy by 23\% over baseline.}
\resumeItemWithoutTitle{Developed a Spring Boot service integrating Gemini 2.0 Flash and Dropbox to generate a dataset of 7,050 summaries with facts, arguments, and statutes via Generative AI APIs.}
\resumeItemWithoutTitle{Achieved a cosine similarity of 31.68\% compared to the Illegal-Bert model from IIT Kharagpur and automated weekly scraping of ˜200 legal cases/month using BeautifulSoup to expand the dataset.}
        \resumeItemListEnd}
      \vspace{2pt}
      \resumeSubHeadingListEnd

\vspace{-5pt}

%-----------Awards-----------------
\section{Achievements}
\resumeSubHeadingListStart
\resumeSubItem{Solved 1500+ DSA problems on LeetCode (top 7.89\%, rating 1793) and 550+ on CodeChef.}{}
\vspace{-5pt}
\resumeSubItem{Top 5\% among 5000+ in Adobe’s GenSolve Hackathon, showcasing strong team collaboration.}{}
\vspace{-5pt}
\resumeSubItem{Secured 3rd rank (NITH) in Codekaze with an AIR 717.}{}
\vspace{-5pt}
\resumeSubItem{Runner-Up in Inter-Year Table Tennis Doubles, 2025 at NIT Hamirpur.}{}
\vspace{-5pt}
\resumeSubHeadingListEnd


\end{document}
