\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{same}
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Tight bullet control
\setlist[itemize]{leftmargin=0.18in,itemsep=2pt,topsep=2pt}

\newcommand{\resumeItem}[1]{
  \item \small{#1}
}

\newcommand{\projectHeading}[2]{
  \vspace{4pt}
  \textbf{#1} \\
  \textit{#2}
  \vspace{2pt}
}

\begin{document}

%-------------------- Header --------------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\LARGE Keshav Mittal} & Email: \href{mailto:keshav.mittal1105@gmail.com}{keshav.mittal1105@gmail.com} \\
  \href{https://github.com/keshav-mittal}{github.com/keshav-mittal} & Mobile: +91-9413514915 \\
\end{tabular*}

%-------------------- Education --------------------
\section{Education}
\textbf{National Institute of Technology, Hamirpur} \hfill Hamirpur, India \\
\textit{Bachelor of Technology in Computer Science and Engineering} \hfill Dec 2021 -- May 2025 \\
\textbf{GPA:} 9.07 / 10.0

%-------------------- Skills --------------------
\section{Skills}
\begin{itemize}
\item \small{\textbf{Languages:} C++, Java, Python, HTML, CSS, JavaScript}
\item \small{\textbf{Frameworks:} Next.js, Spring Boot, React.js, Node.js, Express.js}
\item \small{\textbf{Tools:} Git, GitHub, Postman, Redis, Docker, Kubernetes, Terraform, SOLID, HLD, LLD, OOPS, DBMS, OS, CN}
\item \small{\textbf{Databases:} MongoDB, MySQL, PostgreSQL}
\end{itemize}

%-------------------- Experience --------------------
\section{Experience}

\textbf{Ultimate Kronos Group (UKG)} \hfill Noida, India \\
\textit{Software Development Engineer 1} \hfill Aug 2025 -- Present

\begin{itemize}
\resumeItem{Re-architected a mission-critical payroll API by shifting from cache-based retrieval to PostgreSQL paginated querying (65k row chunks), eliminating timeout failures and reducing infrastructure cost.}
\resumeItem{Created a GitHub Actions workflow to automate GCP secret migrations using Terraform and Python, reducing deployment time by 20 minutes per project.}
\resumeItem{Building an AI diagnostic agent integrating Teams, GitHub, Jira, and PES APIs to accelerate root-cause identification.}
\end{itemize}

\vspace{4pt}

\textbf{WebSonix} \hfill Mumbai, India \\
\textit{Software Developer Intern} \hfill May 2024 -- Nov 2024

\begin{itemize}
\resumeItem{Engineered and deployed a web portal using ReactJS with Firebase backend services.}
\resumeItem{Engaged with 200+ potential customers to support product launch and community growth.}
\resumeItem{Reduced response time from 3 seconds to under 1 second.}
\end{itemize}

%-------------------- Projects --------------------
\section{Projects}

\projectHeading
{ResumeGenie.AI}
{React.js, TypeScript, Node.js, Express.js, Firebase, GenAI, Docker}

\begin{itemize}
\resumeItem{Architected an AI-powered resume platform with PDF parsing, LaTeX editing, and role-specific suggestions.}
\resumeItem{Designed RESTful APIs delivering 25 highly matched job recommendations per call.}
\resumeItem{Integrated Firebase Auth and Firestore for secure resume management.}
\resumeItem{Built an n8n-based AI agent scraping live job listings with 70\%+ resume–JD match.}
\end{itemize}

\vspace{4pt}

\projectHeading
{Legal-text Summarizer}
{Python, Spring Boot, HuggingFace, GenAI, Dropbox}

\begin{itemize}
\resumeItem{Fine-tuned a T5-based model improving summarization accuracy by 23\%.}
\resumeItem{Built a Spring Boot service generating 7,050 AI-powered summaries.}
\resumeItem{Automated scraping of 200+ cases/month using BeautifulSoup.}
\end{itemize}

%-------------------- Achievements --------------------
\section{Achievements}

\begin{itemize}
\item \small{Solved 1500+ DSA problems on LeetCode (Top 7.89\%, rating 1793) and 550+ on CodeChef.}
\item \small{Top 5\% among 5000+ participants in Adobe’s GenSolve Hackathon.}
\item \small{Secured 3rd Rank (NITH) in Codekaze with AIR 717.}
\item \small{Runner-Up in Inter-Year Table Tennis Doubles, 2025.}
\end{itemize}

\end{document}