\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{same}
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item \small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\begin{document}

%-------------------- Header --------------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\LARGE Keshav Mittal} & Email: \href{mailto:keshav.mittal1105@gmail.com}{keshav.mittal1105@gmail.com} \\
  \href{https://github.com/keshav-mittal}{github.com/keshav-mittal} & Mobile: +91-9413514915 \\
\end{tabular*}

%-------------------- Education --------------------
\section{Education}
\begin{itemize}[leftmargin=0.15in]
  \resumeSubheading
    {National Institute of Technology, Hamirpur}{Hamirpur, India}
    {Bachelor of Technology in Computer Science and Engineering}{Dec 2021 -- May 2025}
  \item \small{\textbf{GPA:} 9.07 / 10.0}
\end{itemize}

%-------------------- Skills --------------------
\section{Skills}
\begin{itemize}[leftmargin=0.15in]
  \small{
    \item \textbf{Languages:} C++, Java, Python, HTML, CSS, JavaScript
    \item \textbf{Frameworks:} Next.js, Spring Boot, React.js, Node.js, Express.js
    \item \textbf{Tools:} Git, GitHub, Postman, Redis, Docker, Kubernetes, Terraform, SOLID, HLD, LLD, OOPS, DBMS, OS, CN
    \item \textbf{Databases:} MongoDB, MySQL, PostgreSQL
  }
\end{itemize}

%-------------------- Experience --------------------
\section{Experience}
\begin{itemize}[leftmargin=0.15in]

  \resumeSubheading
    {Ultimate Kronos Group (UKG)}{Noida, India}
    {Software Development Engineer 1}{Aug 2025 -- Present}

    \resumeItemListStart
      \resumeItem{Re-architected a mission-critical payroll API by shifting from cache-based retrieval to PostgreSQL paginated querying (65k row chunks), eliminating timeout failures and reducing infrastructure cost.}
      \resumeItem{Created a GitHub Actions workflow to automate GCP secret migrations using Terraform and Python, reducing deployment time by 20 minutes per project.}
      \resumeItem{Building an AI diagnostic agent integrating Teams, GitHub, Jira, and PES APIs to surface swarm issues and accelerate root-cause identification.}
    \resumeItemListEnd

  \resumeSubheading
    {WebSonix}{Mumbai, India}
    {Software Developer Intern}{May 2024 -- Nov 2024}

    \resumeItemListStart
      \resumeItem{Engineered and deployed a web portal using ReactJS with Firebase backend services.}
      \resumeItem{Engaged with 200+ potential customers, contributing to product launch preparation and community growth.}
      \resumeItem{Optimized system performance, reducing response time from 3 seconds to under 1 second.}
    \resumeItemListEnd

\end{itemize}

%-------------------- Projects --------------------
\section{Projects}
\begin{itemize}[leftmargin=0.15in]

  \resumeSubheading
    {ResumeGenie.AI}{}
    {React.js, TypeScript, Node.js, Express.js, Firebase, GenAI, Docker}{}

    \resumeItemListStart
      \resumeItem{Architected an AI-powered resume platform with PDF parsing, LaTeX editing, and role-specific suggestions.}
      \resumeItem{Designed RESTful APIs delivering 25 highly matched job recommendations per call.}
      \resumeItem{Integrated Firebase Auth for secure Google login and Firestore for managing editable LaTeX templates.}
      \resumeItem{Developed an n8n-based AI agent scraping live job listings with 70\%+ resume–JD match and direct application links.}
    \resumeItemListEnd

  \resumeSubheading
    {Legal-text Summarizer}{}
    {Python, Spring Boot, HuggingFace, GenAI, Dropbox}{}

    \resumeItemListStart
      \resumeItem{Fine-tuned a T5-based model for legal text summarization, improving accuracy by 23\% over baseline.}
      \resumeItem{Built a Spring Boot service integrating Gemini 2.0 Flash and Dropbox to generate 7,050 AI-generated summaries.}
      \resumeItem{Achieved 31.68\% cosine similarity vs Illegal-BERT (IIT Kharagpur) and automated scraping of 200+ cases/month using BeautifulSoup.}
    \resumeItemListEnd

\end{itemize}

%-------------------- Achievements --------------------
\section{Achievements}
\begin{itemize}[leftmargin=0.15in]
  \item \small{Solved 1500+ DSA problems on LeetCode (Top 7.89\%, rating 1793) and 550+ on CodeChef.}
  \item \small{Top 5\% among 5000+ participants in Adobe’s GenSolve Hackathon.}
  \item \small{Secured 3rd Rank (NITH) in Codekaze with AIR 717.}
  \item \small{Runner-Up in Inter-Year Table Tennis Doubles, 2025 at NIT Hamirpur.}
\end{itemize}

\end{document}