
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}


\begin{center}
    {\Huge \scshape Keshav Mittal} \\ \vspace{1pt}
    Noida, INDIA \\ 
    \small \href{mailto:keshav.mittal1105@gmail.com}{keshav.mittal1105@gmail.com} $|$ 
    \href{tel:+91-9413514915}{+91-9413514915} $|$ 
    \href{https://linkedin.com/in/keshav-mittal}{LinkedIn} $|$
    \href{https://github.com/keshav-mittal}{GitHub}
\end{center}


\section{Education}
\resumeSubHeadingListStart

      \resumeSubheading
      {National Institute of Technology, Hamirpur}{Hamirpur}
      {Bachelor of Technology in Computer Science and Engineering}{Dec 2021 -- May 2025}
      \resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart

      \resumeSubheading
      {Ultimate Kronos Group (UKG)}{Noida, INDIA}
      {Software Development Engineer 1}{Aug 2025 -- Present}
      \resumeItemListStart
      \resumeItem{Re-architected a mission-critical payroll API by shifting from cache-based retrieval to PostgreSQL paginated querying (65k row chunks), eliminating timeout failures and reducing infrastructure cost.}
\resumeItem{Created a GitHub Actions workflow to automate GCP secret migrations using Terraform, Python; required for the Deploy Service pipeline and project creation on GCP saved time (20 min/project).}
\resumeItem{Building an AI diagnostic agent integrating Teams, GitHub, Jira, and PES APIs to surface swarm issues and accelerate root-cause identification.}
\resumeItemListEnd

      \resumeSubheading
      {WebSonix}{Mumbai, INDIA}
      {Software Developer Intern}{May 2024 -- Nov 2024}
      \resumeItemListStart
      \resumeItem{Engineered and deployed an innovative web portal using ReactJS with Firebase backend services.}
\resumeItem{Interacted with 200+ potential customers, preparing the product for launch and building community interest.}
\resumeItem{Optimized performance by reducing response time from 3s to under 1s.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart

      \resumeProjectHeading
      {\textbf{ResumeGenie.AI} $|$ \emph{React.js, TypeScript, Node.js, Express.js, shadcn/ui, Firebase, GenAI, Docker}}{}
      \resumeItemListStart
      \resumeItem{Architected an AI-powered resume platform with PDF parsing, LaTeX editing, and role-specific suggestions.}
\resumeItem{Designed RESTful APIs in Node.js/Express for resume parsing and AI scoring, delivering 25 highly matched job recommendations per call.}
\resumeItem{Integrated Firebase Auth for secure Google login and Firestore for managing editable LaTeX resume template.}
\resumeItem{Crafted an n8n-based AI agent that scrapes live job listings with 70\%+ resume–JD match and surfaces direct application links.}
\resumeItemListEnd

      \resumeProjectHeading
      {\textbf{Legal-text Summarizer} $|$ \emph{Python, Spring Boot, HuggingFace, GenAI, Dropbox}}{}
      \resumeItemListStart
      \resumeItem{Fine-tuned a T5-based model for legal-text summarization through data preprocessing and task-specific training, improving summarization accuracy by 23\% over baseline.}
\resumeItem{Developed a Spring Boot service integrating Gemini 2.0 Flash and Dropbox to generate a dataset of 7,050 summaries with facts, arguments, and statutes via Generative AI APIs.}
\resumeItem{Achieved a cosine similarity of 31.68\% compared to the Illegal-Bert model from IIT Kharagpur and automated weekly scraping of ˜200 legal cases/month using BeautifulSoup to expand the dataset.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
\textbf{Languages}{: C++, Java, Python, HTML, CSS, JavaScript} \\ 
\textbf{Frameworks}{: Next.js, Spring Boot, React.js, Node.js, Express.js} \\ 
\textbf{Developer Tools}{: Git, GitHub, Postman, Redis, Docker, Kubernetes, Terraform, SOLID, HLD, LLD, OOPS, DBMS, OS, CN} \\ 
\textbf{Libraries/Databases}{: MongoDB, MySQL, PostgreSQL} 
    }}
\end{itemize}


\end{document}
