%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Auto-generated from form data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-reversed}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Keshav Mittal}{ %\urlstyle{same}\href{http://example.com}{example.com}| \href{http://example2.co}{example2.co}\\
\href{mailto:keshav.mittal1105@gmail.com}{keshav.mittal1105@gmail.com} | \href{tel:919413514915}{+91-9413514915}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN ONE (Left - 60%)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.60\textwidth}

\section{Experience}
\runsubsection{Ultimate Kronos Group (UKG)}
\descript{| Software Development Engineer 1 }
\location{Aug 2025 – Present | Noida, INDIA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Re-architected a mission-critical payroll API by shifting from cache-based retrieval to PostgreSQL paginated querying (65k row chunks), eliminating timeout failures and reducing infrastructure cost.
\item Created a GitHub Actions workflow to automate GCP secret migrations using Terraform, Python; required for the Deploy Service pipeline and project creation on GCP saved time (20 min/project).
\item Building an AI diagnostic agent integrating Teams, GitHub, Jira, and PES APIs to surface swarm issues and accelerate root-cause identification.
\end{tightemize}
\sectionsep

\runsubsection{WebSonix}
\descript{| Software Developer Intern }
\location{May 2024 – Nov 2024 | Mumbai, INDIA}
\begin{tightemize}
\item Engineered and deployed an innovative web portal using ReactJS with Firebase backend services.
\item Interacted with 200+ potential customers, preparing the product for launch and building community interest.
\item Optimized performance by reducing response time from 3s to under 1s.
\end{tightemize}
\sectionsep

\section{Projects}
\runsubsection{ResumeGenie.AI}
\descript{| React.js, TypeScript, Node.js, Express.js, shadcn/ui, Firebase, GenAI, Docker}
\begin{tightemize}
\item Architected an AI-powered resume platform with PDF parsing, LaTeX editing, and role-specific suggestions.
\item Designed RESTful APIs in Node.js/Express for resume parsing and AI scoring, delivering 25 highly matched job recommendations per call.
\item Integrated Firebase Auth for secure Google login and Firestore for managing editable LaTeX resume template.
\item Crafted an n8n-based AI agent that scrapes live job listings with 70\%+ resume–JD match and surfaces direct application links.
\end{tightemize}
\sectionsep

\runsubsection{Legal-text Summarizer}
\descript{| Python, Spring Boot, HuggingFace, GenAI, Dropbox}
\begin{tightemize}
\item Fine-tuned a T5-based model for legal-text summarization through data preprocessing and task-specific training, improving summarization accuracy by 23\% over baseline.
\item Developed a Spring Boot service integrating Gemini 2.0 Flash and Dropbox to generate a dataset of 7,050 summaries with facts, arguments, and statutes via Generative AI APIs.
\item Achieved a cosine similarity of 31.68\% compared to the Illegal-Bert model from IIT Kharagpur and automated weekly scraping of ˜200 legal cases/month using BeautifulSoup to expand the dataset.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN TWO (Right - 33%)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.33\textwidth}

\section{Education}

\subsection{National Institute of Technology, Hamirpur}
\descript{Bachelor of Technology in Computer Science and Engineering}
\location{Dec 2021 - May 2025 | Hamirpur}
\location{ Cum. GPA: 9.07 / 10.0}
\sectionsep

\section{Skills}
\subsection{Programming Languages}
C++ \textbullet{} Java \textbullet{} Python \textbullet{} HTML \textbullet{} CSS \textbullet{} JavaScript \\
\sectionsep

\subsection{Frameworks \& Libraries}
Next.js \textbullet{} Spring Boot \textbullet{} React.js \textbullet{} Node.js \textbullet{} Express.js \\
\sectionsep

\subsection{Tools \& Technologies}
Git \textbullet{} GitHub \textbullet{} Postman \textbullet{} Redis \textbullet{} Docker \textbullet{} Kubernetes \textbullet{} Terraform \textbullet{} SOLID \textbullet{} HLD \textbullet{} LLD \textbullet{} OOPS \textbullet{} DBMS \textbullet{} OS \textbullet{} CN \\
\sectionsep

\subsection{Databases}
MongoDB \textbullet{} MySQL \textbullet{} PostgreSQL \\
\sectionsep

\section{Links}
Github:// \href{https://github.com/keshav-mittal}{\bf keshav-mittal} \\
LinkedIn://  \href{https://linkedin.com/in/keshav-mittal}{\bf keshav-mittal} \\
LeetCode://  \href{https://leetcode.com/keshav-mittal}{\bf keshav-mittal} \\
CodeChef://  \href{https://www.codechef.com/users/keshav-mittal}{\bf keshav-mittal} \\
\sectionsep

\section{Certifications}
AWS Certificate - Amazon Web Service (12 jan  2026) \\
\sectionsep

\section{Achievements}
Solved 1500+ DSA problems on LeetCode (top 7.89\%, rating 1793) and 550+ on CodeChef. \\
Top 5\% among 5000+ in Adobe’s GenSolve Hackathon, showcasing strong team collaboration. \\
Secured 3rd rank (NITH) in Codekaze with an AIR 717. \\
Runner-Up in Inter-Year Table Tennis Doubles, 2025 at NIT Hamirpur. \\
\sectionsep

\end{minipage}
\end{document}